Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-27 paper/paper.qmd
stash

aur_table <- read_excel(here::here("data/aurignacian-periods.xlsx"))

@@

```{r}
## clean the data
library(magrittr)
library(rcarbon)
signbase_full <- read_csv(here::here("data/signBase_Version1.0.csv"))
nsites <- signbase_full %>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts <- nrow(signbase_full)
ncountries <- signbase_full %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes <- ncol(signbase_full)

>>>>

aur_table <- read_excel("data/aurignacian-periods.xlsx")

@@

```{r}
## clean the data
library(magrittr)
library(rcarbon)
signbase_full <- read_csv("data/signBase_Version1.0.csv")
nsites <- signbase_full %>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts <- nrow(signbase_full)
ncountries <- signbase_full %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes <- ncol(signbase_full)
